Phenology and Mycorrhizae Manuscript

### 2023-03-20 manuscriptCode_phenologyAndMycorrhizae.Rmd
Updated to allow for more DD baselines

if(downloadData){
  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
```

@@

for(f in seq_along(funTypes)){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName[f])
}

>>>>

if(downloadData){
  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
combineNEONdata_PhenoObs(saveType="firstOfPhenophase")
combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
combineNEONdata_PhenoObs(saveType="allStatusPhenophase",p=2)
combineNEONdata_PhenoObs(saveType="allStatusPhenophase",p=3)
```

@@

for(f in seq_along(funTypes)){
  # calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
}
